PANCHANGE_analysis

### 2021-03-09 PANCHANGE_analysis.Rmd
hashed out unneeded forest plots for size

lm.forest(plot.dat.disorder,"Predictors of pandemic symptoms")

@@

lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")

@@

lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")

@@

lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")

@@

lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")

@@

lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")

@@

lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")

@@

lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")

@@

lm.forest(plot.dat.noexplan.sample.gad  ,"Predictors of anxiety across samples")

@@

lm.forest(plot.dat.noexplan.sample.phq  ,"Predictors of depression across samples")

@@

lm.forest(plot.dat.noexplan.sample.pcl  ,"Predictors of symptoms of PTSD across samples")

>>>>

#lm.forest(plot.dat.disorder,"Predictors of pandemic symptoms")

@@

#lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")

@@

#lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")

@@

#lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")

@@

#lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")

@@

#lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")

@@

#lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")

@@

#lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")

@@

#lm.forest(plot.dat.noexplan.sample.gad  ,"Predictors of anxiety across samples")

@@

#lm.forest(plot.dat.noexplan.sample.phq  ,"Predictors of depression across samples")

@@

#lm.forest(plot.dat.noexplan.sample.pcl  ,"Predictors of symptoms of PTSD across samples")
